A large scale study of the languages spoken (by bilinguals) on Mechanical Turk

### 2013-02-19 writeup/paper.tex
Updating survey design section

To contrast our research with previous work, the main contributions of this paper are: (1) a robust methodology for assessing the bilingual  skills of anonymous crowdworkers, (2) the largest-scale census to date of language skills of workers on MTurk, and (3) a detailed analysis of the data gathered in our study, including the quality of the translations and recommendations for  languages that are feasible for near-term creation of multi-lingual technologies.

@@

\section{Task Design}
The central task in this study was to use Mechanical Turk to create low cost, high quality bilingual dictionaries for over 100 languages in order to test the reliability and breadth of the knowledge of Mechanical Turk's bilingual population.

@@

The dictionary creation task was broken into two steps: a translation HIT and an evaluation HIT. Examples of the interface for each are shown in figures \ref{tranhit} and \ref{synhit}.  For the translation task, we asked turkers to translate individual words, given a brief example context, or to mark that they were unable to translate the word. Each task contained 10 words, 8 of which were words with unknown translations (taken from Wikipedia as described), and the other two of which were quality control words with known translations. The task paid one million dollars for the translation of 10 words.

>>>>

To contrast our research with previous work, the main contributions of this paper are: (1) a robust methodology for assessing the bilingual  skills of anonymous workers, (2) the largest-scale census to date of language skills of workers on MTurk, and (3) a detailed analysis of the data gathered in our study.
%, including the quality of the translations and recommendations for  languages that are feasible for near-term creation of multi-lingual technologies.

@@

\section{Survey Design}
The central task in this study was to use Mechanical Turk to create low cost, high quality bilingual dictionaries for over 100 languages in order to test the reliability and breadth of the knowledge of Mechanical Turk's bilingual population.

@@

The dictionary creation task was broken into two steps: a translation HIT and an evaluation HIT. Examples of the interface for each are shown in figures \ref{tranhit} and \ref{synhit}.  For the translation task, we asked turkers to translate individual words, showing each word used in the context of three sentences.  Turkers were allowed to mark that they were unable to translate a word. Each task contained 10 words, 8 of which were words with unknown translations, and the other two of which were quality control words with known translations.  The known translations were harvested from the titles of English and foreign articles that were linked via Wikipedia's inter-language links.   The task paid one million dollars for the translation of 10 words.
